Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/relwk.tex
checkpoint more relwk

\paragraph{Application use of parsers.}
Generated parsers have long been used to parse human input, such as programming languages and
configuration files. Frequently, such languages are often specified with a formal grammar in an
executable form. Unfortunately,  parser frameworks are seldom used  to recognize
machine-created input.

A notable exception is the Mongrel
web server~\cite{mongrel} which uses a grammar
for HTTP written in the Ragel~\cite{ragel-paper} regular expression
language. Mongrel was re-written from scratch multiple times to achieve
better scalability and design, yet the grammar could be  re-used across
all iterations~\cite{patterson-citation}.

\paragraph{Other vulnerability mitigations.}

>>>>

\paragraph{Application use of parsers.}

Generated parsers have long been used to parse human input, such
as programming languages and configuration files. Frequently, such
languages are often specified with a formal grammar in an executable
form. Unfortunately, parser frameworks are seldom used to recognize
machine-created input; as we demonstrate in \S\ref{s:eval},
state-of-the-art parser generators are not suitable for parsing or
generating many real-world data formats.

A notable exception is the Mongrel web server~\cite{mongrel} which
uses a grammar for HTTP written in the Ragel regular expression
language~\cite{ragel-paper}.  Mongrel was re-written from scratch
multiple times to achieve better scalability and design, yet the
grammar was reused across all iterations~\cite{patterson-citation}.
We hope that Nail's ideas make it possible to handle a wider range of
protocols using parser generators, and to build more applications on
top of grammar-based parsers.

\paragraph{Vulnerability mitigation.}
